Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex
Added more text to "Results", described auto-k-means

\subsection{Evaluation measures}

@@

The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}. It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.

\paragraph{Clustering.}
The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens. The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in task \emph{c} it was unknown. We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks. In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically. In the second variant we used k-means for clustering in all tasks, and tried our modification of k-means, which we called Auto-k-means in task \emph{c}. The reason for choosing those algorithms is described in section \ref{sec:experimental-results}

@@

Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation. Finally, from all results on training set we chose (eps=0.23, min\_samples=64, metric=cosine) for the final hyperparameters. This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.

@@

\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words). The length of the sliding window is set to $120$ characters. Model B uses k-means clustering. We have chosen two trainable feature transformations: linear and elementwise linear. For the both transformations $5\times 10^{-4}$ was chosen for the learning rate. All the hyperparameters are selected manually by  experimenting on the development dataset, which is approximately $70\%$ of the available dataset. $70\%$ of the development set was used for training basic feature extractors and the transformation. Considering the results on the   validation part of the development set, not very large numbers of iterations seem to be more beneficial. A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation. For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be archivable using smaller numbers like $20$, making training and clustering faster.

@@

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.29 & 0.19 & 0.22 & 0.28 & 0.15 & 0.17 \\
			\citet{sittar-2016} 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
			\midrule			
			Model A 				&  &  &  &  &  & \\			
			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

@@

\begin{table*}
	\caption{Results on the author diarization task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

>>>>

\subsection{Evaluation measures} \label{subsec:evaluation-measures}

@@

The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}. Parameters are randomly initialized with values from a truncated normal distribution withe standard deviation $0.1$. It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.

\paragraph{Clustering.}
The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens. The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in task \emph{c} it was unknown. We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks. In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically. In the second variant we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule. This is described in more detail in section \ref{sec:experimental-results}.

@@

Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation. Finally, from all results on training set we chose (eps=$0.23$, min\_samples=64, metric=cosine) for the final hyperparameters. This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.

@@

\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words). The length of the sliding window is set to $120$ characters. Model B uses k-means clustering. We have chosen two trainable feature transformations: linear and elementwise linear (weighting). For both of the transformations $5\times 10^{-4}$ was chosen for the learning rate. All the hyperparameters are selected manually by  experimenting on the development dataset, which is approximately $70\%$ of the available dataset. $70\%$ of the development set was used for training basic feature extractors and the transformation. Considering the results on the validation part of the development set, not very large numbers of iterations seem to be more beneficial. A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation. For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be achievable using smaller numbers like $20$, making training and clustering faster.

For task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors. It computes the k-means error for each number $k$ in the specified range for the number of clusters. Based on ratios of relative improvements in the score between consecutive $k$-s, it chooses the $k$ giving the best ratio modulated with a modulation function dependent on $k$, simply $k^\alpha$ was chosen, where $\alpha$ is selected using linear search. Being limited in time, we didn't put much effort into optimizing the selection of the best number of clusters. Moreover, even if knowing the number of clusters in advance, it seems that even the transformed features are not satisfactory for correct clustering. We notice that using the correct numbers of authors compared to using a fixed $k=2$ results in relative decrease in BCubed precision, recall, and $F_1$-score by factors of $0.95$, $0.64$ and $0.79$ respectively.

\subsection{Evaluation results}

We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.

The results of evaluation for the intrinsic plagiarism problem (task \emph{a}) are shown in table \ref{tab:results-task-a}. For author diarization with known (task \emph{b}) and unknown (task \emph{c}) numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.

@@

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:results-task-a}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.29 & 0.19 & 0.22 & 0.28 & 0.15 & 0.17 \\
			\citet{sittar-2016} 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
			\midrule			
			Model A 				&  &  &  &  &  & \\			
			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

@@

\begin{table*}
	\caption{Results on the author diarization task.}
	\label{tab:results-task-b-c}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}
